Ethnicity sensitive author disambiguation using semi-supervised learning

### 2016-04-29 paper/author_disambiguation.tex
inspirehep/beard

As part of this work, we developed a stand-alone application for author
disambiguation, publicly available online\footnote{\url{https://github.com/glouppe/beard}} for free reuse
or study.
Our implementation builds upon the Python scientific stack, making
use of the Scikit-Learn library \cite{scikitlearn} for the supervised learning
of a linkage function and of SciPy for clustering.
All components of the disambiguation pipeline have been designed to follow the
Scikit-Learn API \cite{scikitlearnAPI}, making them easy to maintain,
understand and reuse.
Our implementation is made to be efficient, exploiting parallelization when available, and ready for production environments.
It is also designed to be runnable in an incremental fashion in which our approach is considered to be scalable. We adopt the blocking phase in order to reduce the computational complexity from $O(N^2)$ to $O(\sum N_i^2)$, which in practice tends to ${O(N)}$ when $N_i << N$. This also means that instead of having to run the disambiguation process on the whole signature set, the process could be run only on specified blocks if desired.

>>>>

As part of this work, we developed a stand-alone application for author
disambiguation, publicly available online\footnote{\url{https://github.com/inspirehep/beard}} for free reuse
or study.
Our implementation builds upon the Python scientific stack, making
use of the Scikit-Learn library \cite{scikitlearn} for the supervised learning
of a linkage function and of SciPy for clustering.
All components of the disambiguation pipeline have been designed to follow the
Scikit-Learn API \cite{scikitlearnAPI}, making them easy to maintain,
understand and reuse.
Our implementation is made to be efficient, exploiting parallelization when available, and ready for production environments.
It is also designed to be runnable in an incremental fashion in which our approach is considered to be scalable. We adopt the blocking phase in order to reduce the computational complexity from $O(N^2)$ to $O(\sum N_i^2)$, which in practice tends to ${O(N)}$ when $N_i << N$. This also means that instead of having to run the disambiguation process on the whole signature set, the process could be run only on specified blocks if desired.
